Process_OlisSpectraJazEmData

### 2024-01-04 Code/Process_OlisJazEmData.Rmd
Fixing code to make this a script to merge and process Olis absorbance and MC emission data.

```{r load libraries, warning = FALSE, echo=FALSE} 
library(tidyverse)
library(lubridate)
library(stringr)
library(broom)
library(knitr)
library(OneR)
library(zoo)
library(strucchange)
library(ggspectra)
library(ggpubr)
library(caret)
library(photobiologyWavebands)
library(reshape2)
library(photobiology)
library(gcookbook)
```

@@

FileEncode <- "UTF-8" 
Delimiter <- ""
HeaderRows <- 0
```

# List and read imported Olis and Jaz files

```{r exported Rmd only first time in session}
list.files(path = DataInOlis, pattern = Project, full.names = TRUE)
list.files(path = DataInJaz, pattern = Project, full.names = TRUE)
```

```{r read imported Olis file}
OLISSpectraFile <- "../Data/ImportedData/ImportedOlisData/Baltic_Photoperiod_Imported_OlisData.Rds"
OLISSpectraFileName <- str_split(string = OLISSpectraFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds")
OLISSpectra <- readRDS(OLISSpectraFile)  %>%
  ungroup()

JazFile <- "../Data/ImportedData/ImportedJazEmData/Baltic_Photoperiod_Imported_JazEmData.Rds"
JazFileName <- str_split(string = JazFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds")
JazData <- readRDS(JazFile)  %>%
  ungroup()
```

# Preparing df for further analysis

```{r round nm}
JazData <- JazData %>%
   mutate(WavelengthRound = round(Wavelength))
colnames(JazData)

>>>>

```{r load libraries, warning = FALSE, echo=FALSE} 
library(tidyverse)
library(lubridate)
library(stringr)
library(broom)
library(knitr)
library(OneR)
library(zoo)
library(strucchange)
library(ggspectra)
library(ggpubr)
library(caret)
library(photobiologyWavebands)
# library(reshape2)
library(photobiology)
# library(gcookbook)
```

@@

# List imported Olis and Jaz files
```{r exported Rmd only first time in session}
list.files(path = DataInOlis, pattern = ".Rds", full.names = TRUE)
list.files(path = DataInJaz, pattern = ".Rds", full.names = TRUE)
```
# Read Olis whole cell absorbance and MultiCulti Jaz emission files
```{r read imported Olis and Jaz file}
OLISSpectraFile <- readRDS(file = file.path(DataInOlis,"PICO_Imported_OlisData.Rds"))

JazEmFile <- readRDS(file = file.path(DataInJaz,"PICO_Imported_JazEmData.Rds"))
```

#Left off here
```{r}
JazEmFile <- JazEmFile %>% 
  filter(MC_SpectralID != "MCMIX004_WW",
         MCSetPar_uE == 30 ) %>% 
  select(-c( FilenameJaz, MC)) %>% 
  unnest(Spectra) %>%  
  group_by(WL) %>% 
  mutate(MC_NormEm = round(Emission / Emission[which.max(Emission)], digits = 4)) %>% 
ungroup()
```

# Preparing df for further analysis
```{r round nm}
JazData <- JazData %>%
   mutate(WavelengthRound = round(Wavelength))
colnames(JazData)
